On the Design, Use and Removal of Eval in R

### 2020-08-20 inst/paper/main.tex
Outline for The Design of Eval

>>>>

There are four different kinds of \texttt{eval} in the \emph{base} package:  \texttt{eval}, \texttt{evalq}, \texttt{eval.parent},  \texttt{local}.
The most important one is \texttt{eval}:

- the four eval functions in base
- the arguments, expr and envir, enclos
- which expressions are evaluated, which ones are left unchanged
